---
title: "Exploratie Aedes Benchmarkdata"
author: "Martijn Dekker & Frederique Zeelenberg"
date: "29-4-2021"
output: ioslides_presentation
transition: slower
logo: Logo.png
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown {data-background=Background.png data-background-size=cover}


This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets {data-background=Background.png data-background-size=cover}

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output {data-background=Background.png data-background-size=cover}

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot {data-background=Background.png data-background-size=cover}

```{r pressure}
plot(pressure)
```

